There are several ideas of giving notification for search item in drawers. For example, sound, fancy display could be used for notifying users.However, we used LED for fulfilling that purpose because LED is more catch more human attraction towards the point where led glowing compared to sound happening at a point. Moreover a display could do the the above mentioned task to notify a place, but displays are not as bright as LED  in lighting condition. Besides, implementing visual feedback system with led is cheaper than above mentioned two options So, we choose the best option, LED that fulfils our objective. Now, the problem is which colour can provide information meaningfully to user. We found red LED is the best option for giving notification about empty drawer, because culturally humans are familiar with red colour as stopping point. For example traffic light. Moreover, we have one more information to pass to user that is search item available in a specific drawer. We choice blue as a representative for that information. The reason of choosing blue is blue is visually near to the colour of green, but blue LED looks brighter than green LED. So, by breaking the cultural analogy we came up idea that a blue light could be good replacement of green light that represent availability or allowed access in real life situation. Furthermore, We allow two users using the system at the same time. We can notify empty drawers to both users by only red LEDs because the users don't have to check the drawers (No collision) if the drawer is already empty. On the other hand, if the tow users' search item is already available we must have to show them which drawer the should check out their desired items. As it mentioned blue will still used  for the for the first user, but for the second user use yellow.  The users are also notified by graphical user interface that which coloured LED give them the hint about their desired items.